---
title: "Controller"
format: html
---

```{r controller-001}
#| include: false
r = redux::hiredis()
r$FLUSHDB()
options(datatable.prettyprint.char = 10L)
```

A **rush** network consists of thousands of workers started on different machines.
This article explains how to start workers in a rush network.
Rush offers three ways to start workers: local workers with `processx`, remote workers with `mirai` and script workers.

# Local Workers {#sec-local-workers}

We use the random search example from the [Rush article](rush.html) to demonstrate how the controller works.

```{r controller-002}
library(rush)

wl_random_search = function(rush) {
  while(rush$n_finished_tasks < 100) {

    xs = list(x1 = runif(1, -5, 10), x2 = runif(1, 0, 15))
    key = rush$push_running_tasks(xss = list(xs))

    ys = list(y = branin(xs$x1, xs$x2))
    rush$push_results(key, yss = list(ys))
  }
}

rush = rsh(
  network = "test-network",
  config = redux::redis_config())
```

## Start Workers {#sec-local-start-workers}

Workers may be initiated locally or remotely.
Local workers run on the same machine as the controller, whereas remote workers operate on separate machines.
The `$start_local_workers()` method initiates local workers using the `processx` package.
The `n_workers` parameter specifies the number of workers to launch.
The `worker_loop` parameter defines the function executed by each worker.
If the `worker_loop` function depends on global variables, these can be provided via the `globals` parameter.
Required packages for the `worker_loop` can be specified using the `packages` parameter.

```{r controller-003}
worker_ids = rush$start_local_workers(
  worker_loop = wl_random_search,
  n_workers = 4)
```

Worker information is accessible through the `$worker_info` method.
Each worker is identified by a `worker_id`.
The `pid` field denotes the process identifier, and the `hostname` field indicates the machine name.
The `remote` column specifies whether the worker is remote, and the `heartbeat` column indicates the presence of a heartbeat process.
Heartbeat mechanisms are discussed in the [Error Handling](#error-handling) section.

```{r controller-004}
#| include: false
Sys.sleep(1)
```

```{r controller-005}
rush$worker_info
```

The `$worker_states` method returns the current state of each worker.
Possible states include `"running"`, `"terminated"`, `"killed"`, and `"lost"`.

```{r controller-006}
rush$worker_states
```

Additional workers may be added to the network at any time.

```{r controller-007}
rush$start_local_workers(
  worker_loop = wl_random_search,
  n_workers = 2)
```

```{r controller-008}
#| include: false
Sys.sleep(1)
```

```{r controller-009}
rush$worker_states
```

## Rush Plan {#sec-local-rush-plan}

When `rush` is integrated into a third-party package, the starting of workers is typically managed by the package itself.
In such cases, users may configure worker options by invoking the `rush_plan()` function.
This function allows explicit specification of the number of workers, the type of workers, and the configuration for connecting to the Redis database.

```{r controller-010}
#| eval: false
rush_plan(n_workers = 4, config = redux::redis_config(), worker_type = "local")
```

## Globals {#sec-local-globals}

Global variables are those defined in the global environment that must also be accessible to workers.
They are specified by name in the `$start_local_workers()` method.
These variables are serialized and stored in the Redis database.
Upon initialization, each worker retrieves the serialized globals from the database and assigns them to its own global environment.

::: {.callout-note}

The maximum size of a Redis string is 512 MiB.
If the serialized globals required by the worker loop exceed this limit, Rush will raise an error.
In scenarios where both the controller and the workers have access to a shared file system, Rush will instead write large objects to disk.
The `large_objects_path` argument of `rush_plan()` specifies the directory used for storing such large objects.

:::


## Stop Worker {#sec-local-stop-worker}

Workers can be stopped individually or all at once.
To terminate a specific worker, the `$stop_workers()` method is invoked with the corresponding `worker_ids` argument.

```{r controller-011}
rush$stop_workers(worker_ids = worker_ids[1])
```

This command terminates the selected worker process.

```{r controller-012}
#| include: false
Sys.sleep(1)
```

```{r controller-013}
rush$worker_states
```

To stop all workers and reset the network, the `$reset()` method is used.

```{r controller-014}
rush$reset()
```

In the preceding example, the optimization process was stopped after 100 iterations.
Alternatively, it is possible to terminate the optimization by sending a terminate signal.
The worker loop must implement the `rush$terminated` flag.
Then the rush controller can terminate the optimization.

```{r controller-015}
wl_random_search = function(rush) {
  while(!rush$terminated) {

    xs = list(x1 = runif(1, -5, 10), x2 = runif(1, 0, 15))
    key = rush$push_running_tasks(xss = list(xs))

    ys = list(y = branin(xs$x1, xs$x2))
    rush$push_results(key, yss = list(ys))
  }
}

rush = rsh(
  network = "test-random-search-terminate",
  config = redux::redis_config())

rush$start_local_workers(
  worker_loop = wl_random_search,
  n_workers = 2)
```

```{r controller-016}
#| include: false
Sys.sleep(1)
```

The random search proceeds as usual.

```{r controller-017}

rush$fetch_finished_tasks()
```

To terminate the optimization, the following command is used.

```{r controller-018}
rush$stop_workers(type = "terminate")
```

The workers are terminated.

```{r controller-019}
#| include: false
Sys.sleep(1)
```

```{r controller-020}
rush$worker_states
```

## Failed Workers {#sec-local-failed-workers}

We simulate a segfault on the worker by killing the worker process.

```{r controller-021}
rush = rsh(network = "test-failed-workers")

wl_failed_worker = function(rush) {
  tools::pskill(Sys.getpid(), tools::SIGKILL)
}
```

Workers are then started using the faulty worker loop.

```{r controller-022}
worker_ids =  rush$start_local_workers(
  worker_loop = wl_failed_worker,
  n_workers = 2)
```

```{r controller-023}
#| include: false
Sys.sleep(1)
```

The `$detect_lost_workers()` method is used to identify failed workers.
When a worker is detected, its state is updated to `"lost"`.

```{r controller-024}
rush$detect_lost_workers()
rush$worker_states
```

## Restart Workers {#sec-local-restart-workers}

Workers that have failed can be restarted using the `$restart_workers()` method.
This method accepts the `worker_ids` of the workers to be restarted.

```{r controller-025}
rush$restart_workers(worker_ids = worker_ids[1])
```

```{r controller-026}
#| include: false
Sys.sleep(1)
```

The first worker is restarted and its state is updated to `"running"`.

```{r controller-027}
rush$worker_states
```

## Log Messages {#sec-local-log-messages}

Workers record all messages generated using the `lgr` package to the database.
The `lgr_thresholds` argument of `$start_local_workers()` specifies the logging level for each logger, e.g. `c(rush = "debug")`.
While enabling log message storage introduces a minor performance overhead, it is valuable for debugging purposes.
By default, log messages are not stored.
To enable logging, workers are started with the desired logging threshold.

```{r controller-028}
rush = rsh(network = "test-log-messages")

wl_log_message = function(rush) {
  lg = lgr::get_logger("rush")
  lg$info("This is an info message from worker %s", rush$worker_id)
}

rush$start_local_workers(
  worker_loop = wl_log_message,
  n_workers = 2,
  lgr_thresholds = c(rush = "info"))
```

```{r controller-029}
#| include: false
Sys.sleep(1)
```

The most recent log messages can be printed as follows.

```{r controller-030}
Sys.sleep(1)
rush$print_log()
```

To retrieve all log entries, use the `$read_log()` method.

```{r controller-031}
rush$read_log()
```

We reset the network.

```{r controller-032}
rush$reset()
```

# Remote Workers {#sec-remote-workers}

The `mirai` package provides a straightforward mechanism for launching `rush` workers on remote machines.
`mirai` manages daemons, which are persistent background processes capable of executing arbitrary R code in parallel.
These daemons communicate with the main session.

```{r controller-033}

```

## Start Workers {#sec-remote-start-workers}

Usually `mirai` is used to start daemons on remote machines but it can also be used to start local daemons.

```{r controller-034}
library(mirai)

daemons(
  n = 2,
  url = host_url()
)

status()
```

Daemons may also be launched on a remote machine via SSH.

```{r controller-035}
#| eval: false
daemons(
  n = 2L,
  url = host_url(port = 5555),
  remote = ssh_config(remotes = "ssh://10.75.32.90")
)
```

On high performance computing clusters, daemons can be started using a scheduler.

```{r controller-036}
#| eval: false
daemons(
  n = 2L,
  url = host_url(),
  remote = remote_config(
    command = "sbatch",
    args = c("--mem 512", "-n 1", "--wrap", "."),
    rscript = file.path(R.home("bin"), "Rscript"),
    quote = TRUE
  )
)
```

We define a worker loop.

```{r controller-037}
wl_random_search = function(rush) {
  while(rush$n_finished_tasks < 100) {

    xs = list(x1 = runif(1, -5, 10), x2 = runif(1, 0, 15))
    key = rush$push_running_tasks(xss = list(xs))

    ys = list(y = branin(xs$x1, xs$x2))
    rush$push_results(key, yss = list(ys))
  }
}

rush = rsh(
  network = "test-network",
  config = redux::redis_config())
```

We start the daemons.
`daemons(0)` stops all daemons.

```{r controller-038}
daemons(0)
daemons(2)
```

```{r controller-039}
#| include: false
Sys.sleep(1)
```

After the daemons are started, we can start the remote workers.

```{r controller-040}
worker_ids = rush$start_remote_workers(
  worker_loop = wl_random_search,
  n_workers = 2)
```

```{r controller-041}
#| include: false
Sys.sleep(1)
```

```{r controller-042}
rush$worker_info
```

## Failed Workers {#sec-remote-failed-workers}

Failed workers started with `mirai` are also detected by the controller.
We simulate a segfault on the worker by killing the worker process.

```{r controller-043}
daemons(0)
daemons(2)

rush = rsh(network = "test-failed-mirai-workers")

wl_failed_worker = function(rush) {
  tools::pskill(Sys.getpid(), tools::SIGKILL)
}

worker_ids = rush$start_remote_workers(
  worker_loop = wl_failed_worker,
  n_workers = 2)
```

```{r controller-044}
#| include: false
Sys.sleep(1)
```

```{r controller-045}
rush$detect_lost_workers()
```

A segmentation fault also terminates the associated `mirai` daemon.
Therefore, it is necessary to restart the daemon before restarting the workers.

```{r controller-046}
daemons(0)
daemons(2)
status()
```

```{r controller-047}
#| include: false
Sys.sleep(1)
```

Workers can then be restarted using the `$restart_workers()` method.

```{r controller-048}
rush$restart_workers(worker_ids)
```

# Script Workers {#sec-script-workers}

The most flexible method for starting workers is to use a script generated with the `$worker_script()` method.
This script can be executed either on the local machine or on a remote machine.
The only requirement is that the machine is capable of running R scripts and has access to the Redis database.

```{r controller-049}
rush = rsh(
  network = "test-script-workers",
  config = redux::redis_config())

rush$worker_script(
  worker_loop = wl_random_search)
```

## Error Handling {#sec-script-error-handling}

Workers started with `processx` or `mirai` are monitored by these packages.
The heartbeat is a mechanism to monitor the status of script workers.
The mechanism consists of a heartbeat key with a set [expiration timeout](https://redis.io/commands/expire/) and a dedicated heartbeat process that refreshes the timeout periodically.
The heartbeat process is started with `callr` and is linked to the main process of the worker.
In the event of a worker's failure, the associated heartbeat process also ceases to function, thus halting the renewal of the timeout.
The absence of the heartbeat key acts as an indicator to the controller that the worker is no longer operational.
Consequently, the controller updates the worker's status to `"lost"`.

Heartbeats are initiated upon worker startup by specifying the `heartbeat_period` and `heartbeat_expire` parameters.
The `heartbeat_period` defines the frequency at which the heartbeat process will update the timeout.
The `heartbeat_expire` sets the duration, in seconds, before the heartbeat key expires.
The expiration time should be set to a value greater than the heartbeat period to ensure that the heartbeat process has sufficient time to refresh the timeout.

```{r controller-050}
rush$worker_script(
  worker_loop = wl_random_search,
  heartbeat_period = 1,
  heartbeat_expire = 3)
```

The heartbeat process is also the only way to kill a script worker.
The `$stop_workers(type = "kill")` method pushes a kill signal to the heartbeat process.
The heartbeat process terminates the main process of the worker.

