---
title: "Error Handling and Debugging"
format: html
---

```{r error_handling-001}
#| include: false
library(rush)
r = redux::hiredis()
r$FLUSHDB()
options(datatable.prettyprint.char = 10L)
options(datatable.print.nrows = 10L)
```

`rush` provides error-handling mechanisms for two failure modes: standard R errors during task evaluation and unexpected worker failures such as crashes or lost connections.
If errors cannot be caught automatically, the worker loop can be debugged locally.

# Simple R Errors {#sec-error-handling-simple}

We use the random search example from the [tutorial](tutorial.html) and introduce a random error with 50% probability.
Within the worker loop, users are responsible for catching errors and marking the corresponding task as `"failed"` using the `$fail_tasks()` method.

```{r error_handling-002}
library(rush)

branin = function(x1, x2) {
  (x2 - 5.1 / (4 * pi^2) * x1^2 + 5 / pi * x1 - 6)^2 + 10 * (1 - 1 / (8 * pi)) * cos(x1) + 10
}

wl_random_search = function(rush, branin) {

  while(rush$n_finished_tasks < 100) {

    xs = list(x1 = runif(1, -5, 10), x2 = runif(1, 0, 15))
    key = rush$push_running_tasks(xss = list(xs))

    tryCatch({
      if (runif(1) < 0.5) stop("Random Error")
      ys = list(y = branin(xs$x1, xs$x2))
      rush$finish_tasks(key, yss = list(ys))
    }, error = function(e) {
      condition = list(message = e$message)
      rush$fail_tasks(key, conditions = list(condition))
    })
  }
}
```

We initialize the network and start the workers.

```{r error_handling-003}
rush = rsh(
  network = "test-simple-error",
  config = redux::redis_config())

mirai::daemons(4)

rush$start_workers(
  worker_loop = wl_random_search,
  n_workers = 4,
  branin = branin)
```

```{r error_handling-004}
#| include: false
Sys.sleep(1)
```

When an error occurs, the task is marked as `"failed"` and the error message is stored in the `"message"` column.
This ensures that errors do not interrupt the overall execution and allows subsequent inspection and reevaluation of failed tasks.

```{r error_handling-005}
rush$fetch_failed_tasks()
```

# Handling Failing Workers {#sec-error-handling-workers}

When a worker fails due to a crash or lost connection, its tasks may remain in the `"running"` state indefinitely.
We simulate a segmentation fault by terminating the worker process.

```{r error_handling-006}
wl_failed_worker = function(rush) {
  xs = list(x1 = runif(1, -5, 10), x2 = runif(1, 0, 15))
  key = rush$push_running_tasks(xss = list(xs))

  tools::pskill(Sys.getpid(), tools::SIGKILL)
}

rush = rsh(
  network = "test-failed-workers",
  config = redux::redis_config())

mirai::daemons(2)

worker_ids = rush$start_workers(
  worker_loop = wl_failed_worker,
  n_workers = 2)
```

```{r error_handling-007}
#| include: false
Sys.sleep(1)
```

The `$detect_lost_workers()` method identifies such workers and updates their state to `"terminated"`.
For workers started with `$start_local_workers()` or `$start_workers()`, lost worker detection works automatically by checking process status.
Workers started via `$worker_script()` require an additional heartbeat mechanism (see the [manager vignette](manager.html#sec-script-error-handling)).

```{r error_handling-008}
rush$detect_lost_workers()
```

When a worker fails, the state of any task it was evaluating is set to `"failed"`.

```{r error_handling-009}
rush$fetch_failed_tasks()
```

# Debugging {#sec-debugging}

When the worker loop fails due to an uncaught error, the loop can be executed locally to reproduce and inspect the failure.
Consider the following worker loop, which generates an error for large values of `x1`.

```{r error_handling-010}
wl_error = function(rush) {

  repeat {
    x1 = runif(1)
    x2 = runif(1)

    xss = list(list(x1 = x1, x2 = x2))

    key = rush$push_running_tasks(xss = xss)

    if (x1 > 0.90) {
      stop("Unexpected error")
    }

    rush$finish_tasks(key, yss = list(list(y = x1 + x2)))
  }
}
```

To debug the worker loop locally, a `RushWorker` instance is instantiated manually and passed as argument to the worker loop.

```{r error_handling-011}
rush_worker = RushWorker$new(network_id = "test-error")

wl_error(rush_worker)
```

When an error is raised in the main process, `traceback()` can be called to examine the stack trace and breakpoints can be set within the worker loop to inspect the program state.
Note that certain errors such as missing packages may not be reproducible locally but can be identified by running the worker loop in a separate process and using `$detect_lost_workers()`.

```{r error_handling-012}
rush = rsh(
  network = "test-error",
  config = redux::redis_config())

mirai::daemons(1)

rush$start_workers(
  worker_loop = wl_error,
  n_workers = 1)
```

```{r error_handling-013}
#| include: false
Sys.sleep(1)
```

```{r error_handling-014}
rush$detect_lost_workers()
```

Output and message logs can be written to files via the `message_log` and `output_log` arguments.

```{r error_handling-015}
rush = rsh(
  network = "test-error",
  config = redux::redis_config())

message_log = tempdir()
output_log = tempdir()

mirai::daemons(1)

worker_ids = rush$start_workers(
  worker_loop = wl_error,
  n_workers = 1,
  message_log = message_log,
  output_log = output_log)

Sys.sleep(5)

readLines(file.path(message_log, sprintf("message_%s.log", worker_ids[1])))
readLines(file.path(output_log, sprintf("output_%s.log", worker_ids[1])))
```
