---
title: "Rush Manager"
format: html
bibliography: references.bib
---

```{r manager-001}
#| include: false
library(rush)
r = redux::hiredis()
r$FLUSHDB()
options(datatable.prettyprint.char = 10L)
```

The `Rush` manager class is responsible for starting, monitoring, and stopping workers within the network.
This vignette describes the three mechanisms for starting workers: `mirai` daemons, local `processx` processes, and portable R scripts.
We advise reading the [tutorial](tutorial.html) first.
We use the random search example from this vignette to demonstrate the manager.

```{r manager-002}
library(rush)

branin = function(x1, x2) {
  (x2 - 5.1 / (4 * pi^2) * x1^2 + 5 / pi * x1 - 6)^2 +
    10 * (1 - 1 / (8 * pi)) * cos(x1) +
    10
}

wl_random_search = function(rush, branin) {
  while(TRUE) {
    xs = list(x1 = runif(1, -5, 10), x2 = runif(1, 0, 15))
    key = rush$push_running_tasks(xss = list(xs))
    ys = list(y = branin(xs$x1, xs$x2))
    rush$finish_tasks(key, yss = list(ys))
  }
}

config = redux::redis_config()

rush = rsh(
  network = "random-search-network",
  config = config)
```

# Starting Workers with mirai {#sec-starting-workers}

The `mirai` package provides a mechanism for launching `rush` workers on local and remote machines.
`mirai` daemons are persistent background processes that execute arbitrary R code in parallel.
Daemons are started using `mirai::daemons()`.
For local daemons, the number of workers is specified.

```{r manager-003}
library(mirai)

daemons(n = 2L)
```

```{r manager-004}
#| include: false
while (mirai::status()$connections < 2) {
  Sys.sleep(0.1)
}
```

After the daemons are started, workers are launched with the `$start_workers()` method.
The `$wait_for_workers()` method blocks until all workers have registered in the network.

```{r manager-005}
worker_ids = rush$start_workers(
  worker_loop = wl_random_search,
  n_workers = 2,
  branin = branin)

rush$wait_for_workers(worker_ids = worker_ids)
```

Worker information is accessible through the `$worker_info` field.
Each worker is identified by a `worker_id`.
The `pid` field denotes the process identifier and the `hostname` field indicates the machine name.
The `remote` column specifies whether the worker is remote and the `heartbeat` column indicates the presence of a heartbeat process.
The `state` column reflects the current worker state, which can be `"running"` or `"terminated"`.

```{r manager-006}
rush$worker_info
```

## Stopping Workers {#sec-local-stop-worker}

Workers can be stopped individually or all at once.
To terminate a specific worker, the `$stop_workers()` method is called with the corresponding `worker_ids`.

```{r manager-007}
rush$stop_workers(worker_ids = worker_ids[1])
```

```{r manager-008}
rush$worker_info
```

To stop all workers and reset the network, the `$reset()` method is used.

```{r manager-009}
rush$reset()
```

Instead of killing the worker processes, the manager can send a terminate signal.
The worker then terminates after completing its current task.
The worker loop must check the `rush$terminated` flag.

```{r manager-010}
wl_random_search = function(rush, branin) {
  while(!rush$terminated) {
    xs = list(x1 = runif(1, -5, 10), x2 = runif(1, 0, 15))
    key = rush$push_running_tasks(xss = list(xs))
    ys = list(y = branin(xs$x1, xs$x2))
    rush$finish_tasks(key, yss = list(ys))
  }
}

rush = rsh(
  network = "random-search-network",
  config = redux::redis_config())

rush$start_workers(
  worker_loop = wl_random_search,
  n_workers = 2,
  branin = branin)

rush$wait_for_workers(2)
```

```{r manager-011}
rush$fetch_finished_tasks()
```

The `$stop_workers()` method with `type = "terminate"` sends the terminate signal.

```{r manager-012}
rush$stop_workers(type = "terminate")
```

```{r manager-013}
#| include: false
Sys.sleep(1)
```

```{r manager-014}
rush$worker_info
```

```{r manager-015}
rush$reset()
```

## Failed Workers {#sec-remote-failed-workers}

Failed workers started with `mirai` are automatically detected by the manager.
We simulate a worker crash by killing the worker process.

```{r manager-016}
rush = rsh(network = "random-search-network")

wl_failed_worker = function(rush) {
  tools::pskill(Sys.getpid(), tools::SIGKILL)
}
```

```{r manager-017}
mirai::daemons(n = 2L)
```

```{r manager-018}
worker_ids = rush$start_workers(
  worker_loop = wl_failed_worker,
  n_workers = 2L)
```

```{r manager-019}
#| include: false
Sys.sleep(5L)
```

```{r manager-020}
rush$detect_lost_workers()
```

```{r manager-021}
rush$reset()
```

## Remote Workers {#sec-remote-workers}

Daemons can also be launched on remote machines via SSH.

```{r manager-022}
#| eval: false
mirai::daemons(
  n = 2L,
  url = host_url(port = 5555),
  remote = ssh_config(remotes = "ssh://10.75.32.90")
)
```

On high-performance computing clusters, daemons can be started using a scheduler.

```{r manager-023}
#| eval: false
mirai::daemons(
  n = 2L,
  url = host_url(),
  remote = remote_config(
    command = "sbatch",
    args = c("--mem 512", "-n 1", "--wrap", "."),
    rscript = file.path(R.home("bin"), "Rscript"),
    quote = TRUE
  )
)
```

## Rush Plan {#sec-local-rush-plan}

When `rush` is integrated into a third-party package, worker startup is typically managed by the package itself.
Users can configure worker options by calling the `rush_plan()` function, which specifies the number of workers, the worker type, and the Redis configuration.

```{r manager-024}
#| eval: false
rush_plan(n_workers = 2, config = redux::redis_config(), worker_type = "mirai")
```

## Passing Data to Workers {#sec-local-globals}

Arguments required by the worker loop are passed as named arguments to `$start_workers()`.
These arguments are serialized and stored in the Redis database as part of the worker configuration.
Upon initialization, each worker retrieves and deserializes the configuration before executing the worker loop.

::: {.callout-note}

The maximum size of a Redis string is 512 MiB.
If the serialized worker configuration exceeds this limit, `rush` raises an error.
When both the manager and the workers share access to a file system, `rush` will instead write large objects to disk.
The `large_objects_path` argument of `rush_plan()` specifies the directory used for storing such objects.

:::

## Log Messages {#sec-local-log-messages}

Workers can record messages generated via the `lgr` package to the database.
The `lgr_thresholds` argument of `$start_local_workers()` specifies the logging level for each logger, e.g. `c("mlr3/rush" = "debug")`.
Logging introduces a minor performance overhead and is disabled by default.

```{r manager-025}
rush = rsh(network = "random-search-network")

wl_log_message = function(rush) {
  lg = lgr::get_logger("mlr3/rush")
  lg$info("This is an info message from worker %s", rush$worker_id)
}

rush$start_local_workers(
  worker_loop = wl_log_message,
  n_workers = 2,
  lgr_thresholds = c(rush = "info"))
```

```{r manager-026}
#| include: false
Sys.sleep(1)
```

The most recent log messages can be retrieved as follows.

```{r manager-027}
Sys.sleep(1)
rush$print_log()
```

To retrieve all log entries, use the `$read_log()` method.

```{r manager-028}
rush$read_log()
```

```{r manager-029}
rush$reset()
```

# Starting Local Workers {#sec-starting-local-workers}

The `$start_local_workers()` method launches workers using the `processx` package on the local machine.
The `n_workers` argument specifies the number of workers to launch and `worker_loop` defines the function executed by each worker.
Additional arguments required by the worker loop are passed as named arguments to `$start_local_workers()`.

```{r manager-030}
rush = rsh(
  network = "random-search-network",
  config = redux::redis_config())

worker_ids = rush$start_local_workers(
  worker_loop = wl_random_search,
  branin = branin,
  n_workers = 2)

rush$wait_for_workers(worker_ids = worker_ids)
```

```{r manager-031}
rush$worker_info
```

Additional workers can be added to the network at any time.

```{r manager-032}
rush$start_local_workers(
  worker_loop = wl_random_search,
  branin = branin,
  n_workers = 2)

rush$wait_for_workers(worker_ids = worker_ids)
```

```{r manager-033}
rush$worker_info
```

```{r manager-034}
rush$reset()
```

# Script Workers {#sec-script-workers}

The `$worker_script()` method generates an R script that can be executed on any machine with access to the Redis database.
This is the most flexible mechanism for starting workers, as it imposes no constraints on the execution environment.

```{r manager-035}
rush = rsh(
  network = "random-search-network",
  config = redux::redis_config())

rush$worker_script(
  worker_loop = wl_random_search)
```

## Error Handling {#sec-script-error-handling}

Workers started with `processx` and `mirai` are monitored automatically by the respective packages.
Script workers require an explicit heartbeat mechanism to detect failures.
The heartbeat consists of a Redis key with a set expiration timeout, refreshed periodically by a background process linked to the main worker process.
If the worker fails, the heartbeat process also ceases, the key expires, and the manager marks the worker as `"terminated"`.

The `heartbeat_period` and `heartbeat_expire` arguments configure the heartbeat at startup.
The `heartbeat_period` defines the refresh interval in seconds; `heartbeat_expire` sets the expiration duration, which must exceed the heartbeat period.

```{r manager-036}
rush$worker_script(
  worker_loop = wl_random_search,
  heartbeat_period = 1,
  heartbeat_expire = 3)
```

To kill a script worker, the `$stop_workers(type = "kill")` method pushes a kill signal to the heartbeat process, which then terminates the main worker process.
