---
title: "Quick Reference"
format: html
vignette: >
  %\VignetteIndexEntry{Quick Reference}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

A quick reference cheatsheet for `rush`.

# Basic Example

```{r}
library(rush)

config = redux::redis_config()

rush = rsh(network_id = "my_network", config = config)

worker_loop = function(rush) {
  while (rush$n_finished_tasks < 100) {

    xs = list(x = runif(1))
    key = rush$push_running_tasks(xss = list(xs))

    ys = list(y = sqrt(xs$x))
    rush$finish_tasks(key, yss = list(ys))
  }
}

mirai::daemons(2)

rush$start_workers(
  worker_loop = worker_loop,
  n_workers = 2)
```

# Rush Manager {#sec-rush-manager}

```{r}
library(rush)

config = redux::redis_config()

rush = rsh(network_id = "my_network", config = config)
rush
```

The `rsh()` function returns a `Rush` manager object used to start workers, push tasks, and retrieve results.
Multiple networks can run in parallel on the same Redis instance using different network IDs.

# Worker Loop

The worker loop is the function executed by each worker.
It receives a `RushWorker` object as its first argument and runs until the stopping condition is met.

```{r}
worker_loop = function(rush) {
  while (!rush$terminated) {

    xs = list(x = runif(1))
    key = rush$push_running_tasks(xss = list(xs))

    ys = list(y = sqrt(xs$x))
    rush$finish_tasks(key, yss = list(ys))
  }
}
```

# Tasks

Tasks are the unit of work exchanged between workers via Redis.

| Component   | Description                                          |
|-------------|------------------------------------------------------|
| `key`       | Unique task identifier                               |
| `xs`        | Named list of inputs                                 |
| `ys`        | Named list of results                                |
| `state`     | `"queued"`, `"running"`, `"finished"`, or `"failed"` |
| `worker_id` | ID of the worker that ran the task                   |


# Start Workers

```{r}
rush$start_workers(
  worker_loop = worker_loop,
  n_workers = 2)
```

# Stop Workers

```{r}
rush$stop_workers(type = "kill")
```


## Fetch Tasks

Retrieve tasks by state as a `data.table`:

```{r}
rush$fetch_finished_tasks()
rush$fetch_running_tasks()
rush$fetch_failed_tasks()
rush$fetch_queued_tasks()
```

Fetch multiple states atomically to avoid duplicates when tasks change state during retrieval:

```{r}
rush$fetch_tasks_with_state(states = c("running", "finished"))
```

# Task State

```{r}
rush$n_queued_tasks
rush$n_running_tasks
rush$n_finished_tasks
rush$n_failed_tasks
```

# Local Workers

Start workers on the local machine using the `processx` package:

```{r}
rush$start_local_workers(
  worker_loop = worker_loop,
  n_workers = 2)
```

# Script Workers

Generate a standalone R script that can be run on any machine with Redis access.
This is the most flexible deployment option.

```{r}
script = rush$worker_script(worker_loop = worker_loop)
cat(script)
```

# Heartbeats

Add a heartbeat to detect crashed script workers:

```{r}
script = rush$worker_script(
  worker_loop = worker_loop,
  heartbeat_period = 10,
  heartbeat_expire = 30)
```

# Task Queues

Push tasks to a central queue for workers to consume:

```{r}
xss = replicate(25, list(x1 = runif(1, -5, 10), x2 = runif(1, 0, 15)), simplify = FALSE)

rush$push_tasks(xss = xss)
```

Pop tasks from the queue in the worker loop:

```{r}
worker_loop = function(rush) {
  repeat {
    task = rush$pop_task()
    if (is.null(task)) break

    ys = list(y = sqrt(task$xs$x))
    rush$push_results(task$key, yss = list(ys))
  }
}
```



## 10. Stop Workers and Reset

Graceful termination (worker loop must check `rush$terminated`):

```r
rush$stop_workers(type = "terminate")
```

Kill workers immediately:

```r
rush$stop_workers(type = "kill")

# Kill specific workers
rush$stop_workers(worker_ids = worker_ids[1:2])
```

Reset the entire network (stops all workers and flushes Redis keys):

```r
rush$reset()
```

## 11. Error Handling

Catch errors in the worker loop and mark tasks as failed:

```r
worker_loop = function(rush) {
  while (!rush$terminated) {

    xs = list(x = runif(1))
    key = rush$push_running_tasks(xss = list(xs))

    tryCatch({
      ys = list(y = some_function(xs$x))
      rush$push_results(key, yss = list(ys))
    }, error = function(e) {
      rush$push_failed(key, conditions = list(list(message = e$message)))
    })
  }
}
```

Failed tasks store the error message and are retrievable:

```r
rush$fetch_failed_tasks()
```

## 12. Detecting Lost Workers

Workers that crash (segfault, OOM, network loss) leave tasks stuck in `"running"`.
Call `$detect_lost_workers()` to identify them and fail their running tasks:

```r
rush$detect_lost_workers()

rush$worker_info
```

This works for local (`processx`) and remote (`mirai`) workers.
Script workers require a heartbeat (see [Script Workers](#script-workers)).

## 13. Debugging

Run the worker loop locally by creating a `RushWorker` manually:

```r
rush_worker = RushWorker$new("test-network", remote = FALSE)

worker_loop(rush_worker)
```

Any error raised locally shows a full traceback.
Enable file logs for workers running in the background:

```r
message_log = tempdir()
output_log = tempdir()

worker_ids = rush$start_local_workers(
  worker_loop = worker_loop,
  n_workers = 1,
  message_log = message_log,
  output_log = output_log)

readLines(file.path(message_log, sprintf("message_%s.log", worker_ids[1])))
```

## 14. Logging

Workers log to Redis using `lgr`.
Enable logging by passing `lgr_thresholds` when starting workers:

```r
rush$start_local_workers(
  worker_loop = worker_loop,
  n_workers = 2,
  lgr_thresholds = c(rush = "info"))
```

Write log messages in the worker loop:

```r
worker_loop = function(rush) {
  lg = lgr::get_logger("mlr3/rush")
  lg$info("Worker %s started on %s", rush$worker_id, rush$hostname)
  ...
}
```

Read logs from the controller:

```r
rush$print_log()   # formatted output
rush$read_log()    # data.table
```

## 15. Rush Plan

When `rush` is embedded in a third-party package, users configure workers via `rush_plan()`:

```r
rush_plan(
  n_workers = 4,
  config = redux::redis_config(),
  worker_type = "local")          # "local" or "mirai"
```

Read back the stored configuration:

```r
rush_config()
rush_available()   # TRUE if config is set
```

Remove the plan:

```r
remove_rush_plan()
```
