---
title: "rush - Quick Reference"
format: html
vignette: >
  %\VignetteIndexEntry{rush}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r rush-001}
#| include: false
r = redux::hiredis()
r$FLUSHDB()
options(datatable.prettyprint.char = 15L)
```

A quick reference cheatsheet for `rush`.
See the [tutorial](tutorial.html) for a detailed introduction.

# Worker Loop

```{r rush-002}
library(rush)

worker_loop = function(rush) {
  while (!rush$terminated) {

    xs = list(x = runif(1L))
    key = rush$push_running_tasks(xss = list(xs))

    ys = list(y = sqrt(xs$x))
    rush$finish_tasks(key, yss = list(ys))
  }
}
```

# Rush Manager

```{r rush-003}
config = redux::redis_config()

rush = rsh(network_id = "my_network", config = config)
rush
```

# Start Workers

```{r rush-004}
mirai::daemons(n = 2L)

rush$start_workers(
  worker_loop = worker_loop,
  n_workers = 2L)
```

# Wait for Workers

```{r rush-005}
rush$wait_for_workers(n = 2L)
```

```{r rush-006}
#| include: false
Sys.sleep(5)
```

# Fetch Results

```{r rush-007}
rush$fetch_finished_tasks()
```

# Stop Workers

```{r rush-008}
rush$stop_workers(type = "kill")
```

# Tasks

| Component   | Description                                          |
|-------------|------------------------------------------------------|
| `key`       | Unique task identifier                               |
| `xs`        | Named list of inputs                                 |
| `ys`        | Named list of results                                |
| `state`     | `"running"`, `"finished"`,`"failed"`, or `"queued"`  |
| `worker_id` | ID of the worker that ran the task                   |

# More fetch methods

```{r rush-009}
rush$fetch_tasks()
rush$fetch_queued_tasks()
rush$fetch_running_tasks()
rush$fetch_failed_tasks()
rush$fetch_tasks_with_state(states = c("running", "finished"))
```

# Task Counts

```{r rush-010}
rush$n_queued_tasks
rush$n_running_tasks
rush$n_finished_tasks
rush$n_failed_tasks
```

# Push Tasks to Queue

```{r rush-011}
xss = replicate(25, list(x = runif(1L)), simplify = FALSE)

rush$push_tasks(xss = xss)
```

# Pop Task from Queue

```{r rush-012}
task = rush$pop_task()
task
```

```{r rush-013}
worker_loop = function(rush) {
  repeat {
    task = rush$pop_task()
    if (is.null(task)) break

    ys = list(y = sqrt(task$xs$x))
    rush$finish_tasks(task$key, yss = list(ys))
  }
}
```

# Local Workers

```{r rush-014}
rush$start_local_workers(
  worker_loop = worker_loop,
  n_workers = 2)
```

# Script Workers

```{r rush-015}
script = rush$worker_script(worker_loop = worker_loop)
cat(script)
```

# Heartbeats

```{r rush-016}
script = rush$worker_script(
  worker_loop = worker_loop,
  heartbeat_period = 10,
  heartbeat_expire = 30)
```

# Reset Network

```{r rush-017}
rush$reset()
```

# Handling R Errors

```{r rush-018}
worker_loop = function(rush) {
  while (!rush$terminated) {

    xs = list(x = runif(1))
    key = rush$push_running_tasks(xss = list(xs))

    tryCatch({
      ys = list(y = some_function(xs$x))
      rush$finish_tasks(key, yss = list(ys))
    }, error = function(e) {
      rush$fail_tasks(key, conditions = list(list(message = e$message)))
    })
  }
}
```

# Detecting Lost Workers

```{r rush-019}
rush$detect_lost_workers()
```

# Logging

```{r rush-020}
worker_loop = function(rush) {
  lg = lgr::get_logger("mlr3/rush")
  lg$info("Worker %s started on %s", rush$worker_id, rush$hostname)
}

rush$start_workers(
  worker_loop = worker_loop,
  n_workers = 2,
  lgr_thresholds = c(rush = "info"))
```

```{r rush-021}
#| include: false
Sys.sleep(5)
```

```{r rush-022}
rush$print_log()
```

# Debugging

```{r rush-023}
rush_worker = RushWorker$new("test-network")

worker_loop(rush_worker)
```

```{r rush-024}
mirai::daemons(1L)

worker_ids = rush$start_workers(
  worker_loop = worker_loop,
  n_workers = 1,
  message_log = "message",
  output_log = "output")
```

# Rush Plan

```{r rush-025}
rush_plan(
  n_workers = 4,
  config = redux::redis_config(),
  worker_type = "mirai")
```
